The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-10-14 outputs/docs/events/paper.Rmd

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. The advantage of using our analysis model is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

>>>>

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. More specifically, we contribute in terms of both data and methods. To the best of our knowledge... **[dataset claim]**. Our dataset is available to other researchers via an accompanying R Package. **[Methods claim...]** The advantage of using our analysis model is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

**[Selling points:]**
**[Almost complete record. Unique word count.]**
**[Different events method.]**
**[Highlight increase in volatility. ADD TO ABSTRACT. DISCUSS IMPLICATIONS IN DISCUSSION. Personality driven.]**
**[Gary King paper?]**
